\section{Item definition}
% Reference: DS/ISO 26262-3 section 5

\subsection{Pre-existing information}
% This section is for further supporting information such as a product idea,
% a project sketch, relevant patents, the results of pre-trials, the documentation
% from predecessor items, relevant information on other independent items.
% Reference: DS/ISO 26262-3 section 5.3.2

The cooling system is a liquid cooling system that cools the motors and the
motor drives container.
The system features a pump that can be controlled from a 5v signal.

\subsection{Functional requirements}
% A functional requirement is a requirement for what the item is supposed
% to accomplish.
% In general, functional requirements can be expressed in the form:
%     The item must do <requirement>
% Functional requirements are best specified by input/output listings,
% a mathemathical model/function or similar behaviour descriptions.
%
% Required information:
%   - Purpose of the item
%   - Functionality of the item, including operating modes and states of the item
%   - Assumptions on expected behaviour of the item
%
% Reference: DS/ISO 26262-3 section 5.4.1

The purpose of the item is to cool the motor and motors drives to prevent overheating.
The item must be able to read the temperature of its reservoir and of the systems being cooled.
The item must feature a way to control the cooling power based on the temperature readings.
The item must always be in an active state of cooling while the tractive system is active.
If the tractive system is disengaged while the vehicle is still on,
the cooling system should still be active.
The cooling system may be shut down when the temperature is low and the
tractive system remains inactive.

\subsection{Non-functional requirements}
% A non-functional requirement is a requirement for how the item should be.
% In general, non-functional requirements can be expressed in the form:
%     The item must be <requirement>
% Non-functional requirements are overall properties of the item such as quality
% requirements and constraints.
%
% Required information:
%    - Operational constraints such as prescribed behaviours for implementation
%    - FSE rule requirements
%
% Recommended information:
%    - Environmental constraints such as temperature and humidity
%    - Behaviour achieved by similar items, if any
%
% Reference: DS/ISO 26262-3 section 5.4.1

The electrical signal controlling the pump must be resistant to the
environmental conditions in the back of the car.

\subsection{Boundary and interfaces}
% Required information:
%    - Elements of the item
%    - Assumptions about item's behaviour on other items
%    - Interactions with other items
%    - Functionality required by other items
%    - Functionality required from other items
%
% Recommended information:
%    - Distribution of functions among the involved systems
%    - Operating scenarios which impact the functionality of the item
%
% Reference: DS/ISO 26262-3 section 5.4.2

The item consists of a pump, a control unit and temperature sensors
in the systems being cooled and the reservoir.
The item should turn of the tractive system incase of overheating.
